### 2024-04-22 manuscript.tex
Fixed some citation and caption issues

The initial studies demonstrating evidence of constraint were generally restricted to specific features or proteins. However, by comparing the observed values of various IDR-associated properties against those generated under a simulated model of evolution, Zarin \textit{et al.} showed most IDRs across the entire yeast proteome contain conserved features. Furthermore, they identified clusters of IDRs with common ``evolutionary signatures,'' \textit{i.e.} patterns of conserved features, which were associated with specific biological functions. This analysis for the first time provided a global view of the relationship between sequence and function in IDRs. A follow-up study then expanded on this initial finding by applying techniques from machine learning and statistics to predict the functions of individual IDRs using their evolutionary signatures~\cite{Zarin2021}.

@@

\begin{figure}[h!]
\includegraphics[width=\textwidth]{clusters/out/clusters.png}
\centering
\caption{\textbf{Example clusters with log likelihood ratios and normalized optimal values.}
Each panel shows the pattern of log likelihood ratios of the indicated cluster from Fig~\ref{fig:hierarchy} in the upper half and the corresponding normalized estimated optimal values in the lower half. The optimal values are expressed as $z$-scores relative to each feature distribution in the subset of rapidly evolving disorder regions clustered in Fig~\ref{fig:hierarchy}. Values below or above negative or positive three are indicated with magenta and cyan, respectively.}
\label{fig:clusters}
\end{figure}

>>>>

The initial studies demonstrating evidence of constraint were generally restricted to specific features or proteins. However, by comparing the observed values of various IDR-associated properties against those generated under a simulated model of evolution, Zarin \textit{et al.}~\cite{Zarin2019} showed most IDRs across the entire yeast proteome contain conserved features. Furthermore, they identified clusters of IDRs with common ``evolutionary signatures,'' \textit{i.e.} patterns of conserved features, which were associated with specific biological functions. This analysis for the first time provided a global view of the relationship between sequence and function in IDRs. A follow-up study then expanded on this initial finding by applying techniques from machine learning and statistics to predict the functions of individual IDRs using their evolutionary signatures~\cite{Zarin2021}.

@@

\begin{figure}[h!]
\includegraphics[width=\textwidth]{clusters/out/clusters.png}
\centering
\caption{\textbf{Example clusters with log likelihood ratios and normalized optimal values.}
\textbf{(A-D)} Each panel shows the pattern of log likelihood ratios of the indicated cluster from Fig~\ref{fig:hierarchy} in the upper half and the corresponding normalized estimated optimal values in the lower half. The optimal values are expressed as $z$-scores relative to each feature distribution in the subset of rapidly evolving disorder regions clustered in Fig~\ref{fig:hierarchy}. Values below or above negative or positive three are indicated with magenta and cyan, respectively.}
\label{fig:clusters}
\end{figure}
